loading/cleaning/wrangling/exploring

### 2024-06-27 hcny_cleaned_updatedMoji.qmd
html update 6:49pm

---
title: "loading/cleaning/wrangling/exploring"
author: "Edward Cruz"
format: docx
---

```{r}
library(readxl)
#update.packages("tidyverse")
library(tidyverse)
#update.packages("dplyr")
library(dplyr)
#update.packages('mgcv')
library(mgcv)
```

@@

```{r}
head(hcny_data)
```
```{r}
str(hcny_data)
```
```{r}
summary(hcny_data)
```
```{r}
view(hcny_data)
```

```{r}
# Merge the first two rows to create a proper header
header <- hcny_data[1:4, ]
header <- sapply(header, function(x) paste(na.omit(x), collapse = " "))
colnames(hcny_data) <- header
head(header)
```

```{r}
# Remove the first two rows (header rows) and any completely blank rows
hcnydata_cleaned <- hcny_data[-c(1,2), ]
head(hcnydata_cleaned)
```
```{r}
# Assuming hcny_data_cleaned is your cleaned data frame
colnames(hcnydata_cleaned) <- c("State", "Varroa_Mites", "Other_Parasites_1/", "Disease_2/", "Pesticides", "Other_3/", "Unknown")
```

@@

```{r}
# Convert specified columns to numeric
hcnydata_cleaned <- hcnydata_cleaned %>%
  mutate(across(c("Varroa_Mites", "Other_Parasites_1/", "Disease_2/", "Pesticides", "Other_3/", "Unknown"), as.numeric))
```

```{r}
# View the updated data frame
hcnydata_cleaned<-hcnydata_cleaned[-1,]
```

```{r}
head(hcnydata_cleaned)
```
```{r}
# Verify the changes
str(hcnydata_cleaned)
```

@@

```{r}
view(hcnydata_cleaned)
```

```{r}
ggplot(hcnydata_cleaned, aes(Varroa_Mites)) + geom_histogram()
```

```{r}
ggplot(hcnydata_cleaned, aes(x = Varroa_Mites)) +
  geom_histogram(binwidth = 1, fill = "blue", color = "black") +
  labs(title = "Histogram of Varroa Mites",
       x = "Varroa Mites",
       y = "Frequency")
```
```{r}
# Example scatter plot of two variables
ggplot(hcnydata_cleaned, aes(x = Varroa_Mites, y = "Desease_2/")) +
  geom_point() +
  labs(title = "Scatter Plot of Varroa Mites vs Disease",
       x = "Varroa Mites",
       y = "2 American and European Foul Brood")
```

```{r}
view(hcnydata_cleaned)
```

```{r}
# Write the cleaned data to a new CSV file
write.csv(hcnydata_cleaned, "C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/docs/hcnydata_cleaned.csv", row.names = FALSE)
```

>>>>

---
title: "loading/cleaning/wrangling/exploring"
author: "Mojisola Popoola, Leonel Salazar, ED Cruz, Amelia"
format: docx
---

```{r, message=FALSE, warning=FALSE}
library(readxl)
library(tidyverse)
library(dplyr)
library(readr)
library(tidymodels)
```

@@

```{r}
head(hcny_data)
```

```{r}
str(hcny_data)
```

```{r}
summary(hcny_data)
```

```{r}
# Step 2: Merge the first two rows to create a new header
new_header <- paste(hcny_data[1, ], hcny_data[2, ], sep = " ")

# Step 3: Set the new header
colnames(hcny_data) <- new_header

# Step 4: Remove the first three rows
hcny_data <- hcny_data[-c(1:3), ]

# Step 5: Remove completely blank rows
hcny_data <- hcny_data[rowSums(hcny_data != "") > 0, ]

# Display the resulting data frame
head(hcny_data)
```

```{r}
# Assuming hcny_data is your cleaned data frame
colnames(hcny_data) <- c("state", "varroa_mites", "other_pests", "disease", "pesticides", "other", "unknown")
```

```{r}
head(hcny_data)
```

```{r}
# Convert specified columns to numeric with warning suppression
hcnydata_cleaned <- hcny_data %>%
  mutate(across(c("varroa_mites", "other_pests", "disease", "pesticides", "other", "unknown"), ~suppressWarnings(as.numeric(.))))

@@

```{r}
# Verify the changes
str(hcnydata_cleaned)
```

@@

```{r,message=FALSE, warning=FALSE}
ggplot(hcnydata_cleaned, aes(varroa_mites)) + geom_histogram()
```

```{r}
view((hcnydata_cleaned))
```

```{r}
# Write the cleaned data to a new CSV file
write.csv(hcnydata_cleaned, "C:/Users/ecruz/OneDrive/Documents/UTSA - Data Science Program/Semester Classes/Practicum II Repository/P2-Practicum-II-Portfolio-EdwardCruz/hcny_CleanDraft.csv", row.names = FALSE)
```
